### 2014-04-01 Docs/flowchart/flowchart.tex
more about the delta_gamma1_term stuff

{\bf React State}$[\rho^{\inp},(\rho                                                                   h)^{\inp},X_k^{\inp},T^{\inp}, (\rho\Hext)^{\inp},                                                      
  p_0^{\inp}] \rightarrow [\rho^{\outp}, (\rho h)^{\outp}, X_k^{\outp},                                   
  T^{\outp}, (\rho \omegadot_k)^{\outp}, (\rho\Hnuc)^{\outp}]$
  evolves the species and enthalpy due to reactions through
  $\Delta t/2$ according to:
\begin{equation}
\frac{dX_k}{dt} = \omegadot_k(\rho,X_k,T) ; \qquad
\frac{dT}{dt}   = \frac{1}{c_p} \left ( -\sum_k \xi_k  \omegadot_k  + \Hnuc \right ).
\end{equation}
%This system is solved using the stiff ordinary differential equation                                     
%integration package, {\tt VODE} \citep{vode}.                                                            
Full details of the
solution procedure can be found in Paper III. We then define:
\begin{eqnarray}
(\rho\omegadot_k)^{\outp} &=& \frac{\rho^{\outp} ( X_k^{\outp} - X_k^{\inp})}{\dt/2}, \\
(\rho h)^{\outp} &=& (\rho h)^{\inp} + \frac{\dt}{2} (\rho\Hnuc)^{\outp} + \frac{\dt}{2} (\rho\Hext)^{\in\
p}.
\end{eqnarray}
where the enthalpy update includes external heat sources $(\rho\Hext)^{\inp}$.
As introduced in Paper IV, we update the temperature using $T^{\outp} =                                   
T(\rho^\outp,h^\outp,X_k^\outp)$ for planar geometry or $T^{\outp} =                                      
T(\rho^\outp,p_0^\inp,X_k^\outp)$ for spherical geometry.
Note that the density remains unchanged within {\bf React State}, i.e.,
$\rho^{\outp} = \rho^{\inp}$.

{\bf Advect Base Density}$[\rho_0^\inp,w_0^\inp] \rightarrow
  [\rho_0^\outp, \rho_0^{\outp,\nph}]$ is the process by which we
  update the base state density through $\dt$ in time.  We keep the
  time-centered edge states, $\rho_0^{\outp,\nph}$,
  since they are used later in discretization of $\etarho$ for planar problems.
\begin{description}
\item[planar:] We discretize equation (\ref{eq:Base State Density}) to
  compute the new base state density,
\begin{equation}
\rho_{0,j}^{\outp} = \rho_{0,j}^{\inp} - \frac{\dt}{\dr} \left [ \left( \rho_0^{\outp,\nph} w_0^{\inp}\right)_{j+\myhalf} - \left( \rho_0^{\outp,\nph} w_0^{\inp}\right)_{j-\myhalf} \right ].
\end{equation}
  We compute the time-centered edge states, $\rho_0^{\outp,\nph}$,
  by discretizing an expanded form of equation (\ref{eq:Base State Density}):
\begin{equation}
\frac{\partial \rho_0}{\partial t} + w_0 \frac{\partial \rho_0}{\partial r} = - \rho_0 \frac{\partial w_0}{\partial r},
\end{equation}
  where the right hand side is used as the force term.
\item[spherical:] The base state density update now includes the area factors in the 
  divergences:
\begin{equation}
\rho_{0,j}^{\outp} = \rho_{0,j}^{\inp} - \frac{1}{r_j^2} \frac{\dt}{\dr} \left [ \left( r^2 \rho_0^{\outp,\nph} w_0^{\inp}\right)_{j+\myhalf} - \left( r^2 \rho_0^{\outp,\nph} w_0^{\inp}\right)_{j-\myhalf} \right].
\end{equation}
  In order to compute the time-centered edge states, an additional geometric 
  term is added to the forcing, due to the spherical discretization of 
  (\ref{eq:Base State Density}):
\begin{equation}
\frac{\partial \rho_0}{\partial t} + w_0 \frac{\partial \rho_0}{\partial r} = - \rho_0 \frac{\partial w_0}{\partial r} - \frac{2 \rho_0 w_0}{r}.
\end{equation}
\end{description}

{\bf Enforce HSE}$[p_0^{\inp},\rho_0^{\inp}]
  \rightarrow [p_0^{\outp}]$ has replaced {\bf Advect Base Pressure}
  from Paper III as the process by which we update the base state
  pressure.  Rather than discretizing the evolution equation for
  $p_0$, we enforce hydrostatic equilibrium directly, which is numerically simpler
  and analytically equivalent.  We first set 
  $p_{0,j=0}^{\outp} = p_{0,j=0}^{\inp}$ and then update $p_0^\outp$ using:
\begin{equation}
p_{0,j+1}^{\outp} = p_{0,j}^{\outp} + \Delta r g_{j+\myhalf}\frac{\left(\rho_{0,j+1}^{\inp}+\rho_{0,j}^{\inp}\right)}{2},
\end{equation}
  where $g=g(\rho_0^\inp)$.  As soon as $\rho_{0,j}^\inp < \rho_{\rm cutoff}$, we set 
  $p_{0,j+1}^\outp = p_{0,j}^\outp$ for all remaining values of $j$.  
  Then we compare $p_{0,j_{\rm max}}^\outp$ with $p_{0,j_{\rm max}}^\inp$ and offset
  every element in $p_0^\outp$ so that $p_{0,j_{\rm max}}^\outp = p_{0,j_{\rm max}}^\inp$.  
  We are effectively using the location where the $\rho_0^\inp$ drops below 
  $\rho_{\rm cutoff}$ as the starting point for integration.

{\bf Advect Base Enthalpy}$[(\rho h)_0^\inp,w_0^\inp,\psi^\inp] \rightarrow [(\rho h)_0^\outp]$
  is the process by which we update the base state enthalpy through $\dt$ in time.  
\begin{description}
\item[planar:] We discretize equation (\ref{eq:Base State Enthalpy}), neglecting reaction source terms,
  to compute the new base state enthalpy,
\begin{equation}
(\rho h)_{0,j}^{\outp} = (\rho h)_{0,j}^{\inp} - \frac{\dt}{\Delta r} \left\{ \left[ (\rho h)_0^{\nph} w_0^{\inp}\right]_{j+\myhalf} - \left[ (\rho h)_0^{\nph} w_0^{\inp}\right]_{j-\myhalf} \right\} + \dt\psi_j^{\inp}.
\end{equation}
  We compute the time-centered edge states, $(\rho h)_0^{\nph}$, by discretizing
  an expanded form of equation (\ref{eq:Base State Enthalpy}):
\begin{equation}
\frac{\partial (\rho h)_0}{\partial t} + w_0 \frac{\partial (\rho h)_0}{\partial r} = -(\rho h)_0 \frac{\partial w_0}{\partial r} + \psi.
\end{equation}
\item[spherical:]  The base state enthalpy update now includes the area factors 
  in the divergences:
\begin{eqnarray}
(\rho h)_{0,j}^{\outp} &=& (\rho h)_{0,j}^{\inp} \nonumber \\
&& - \frac{1}{r_j^2} \frac{\dt}{\dr} \left \{ \left[ r^2 (\rho h)_0^{\nph} w_0^{\inp}\right]_{j+\myhalf} - \left[ r^2 (\rho h)_0^{\nph} w_0^{\inp}\right]_{j-\myhalf} \right\} +\dt\psi^{\inp,\nph}.\nonumber\\
\end{eqnarray}
  In order to compute the time-centered edge states, an additional geometric 
  term is added to the forcing, due to the spherical discretization of 
  (\ref{eq:Base State Enthalpy}):
\begin{equation}
\frac{\partial (\rho h)_0}{\partial t} + w_0 \frac{\partial (\rho h)_0}{\partial r} = -(\rho h)_0 \frac{\partial w_0}{\partial r} - \frac{2 (\rho h)_0 w_0}{r} + \psi.
\end{equation}
\end{description}

\subsubsection{Computing $w_0$}\label{Sec:Computing w0}
Here we describe the process by which we compute $w_0$.  The arguments 
are different for planar and spherical geometries.
\begin{description}

@@

@@

\subsection{$\Gamma_1$ Variation Changes}

@@

These can be written more compactly as:
\begin{equation}
\frac{\partial w_0}{\partial r} = \Sbar -\frac{1}{\gammabar p_0}\psi +
\overline{ \left ( \frac{\delta \Gamma_1}{\gammabar^2 p_0} \ut \cdotb \nablab
  p_0 \right ) } \enskip , \label{eq:base_w0_with_dgamma1}
\end{equation}
for plane-parallel geometries (analogous to eq. [\ref{eq:divw0}]), and
\begin{equation}
\nablab \cdotb (\beta_0 \Ubt) = \beta_0 \left [ S - \Sbar + \frac{\delta
    \Gamma_1}{\gammabar^2 p_0} \psi + \frac{\delta \Gamma_1}{\gammabar^2 p_0}
  \Ubt \cdotb \nablab p_0 - \overline{ \left ( \frac{\delta
      \Gamma_1}{\gammabar^2 p_0} \Ubt \cdotb \nablab p_0 \right ) } ~ \right ]
 \enskip ,  \label{eq:constraint_with_delta_gamma}
\end{equation}

@@

\subsection{Thermal Diffusion Changes}
Immediately after {\bf Step 4H}, diffuse the enthalpy through 
a time interval of $\dt$.  First, define $(\rho h)^{(1a),\star} = (\rho h)^{(2),\star}$.  
We recompute $(\rho h)^{(2),\star}$ to account for thermal diffusion.  Here we begin
with the enthalpy equation, but consider only the 
diffusion terms,
\begin{equation}
\frac{\partial (\rho h)}{\partial t} = \nabla\cdot\kth\nabla T.
  \end{equation}
We can recast this as an enthalpy-diffusion equation by applying the
chain-rule to $h(p_0,T,X_k)$,
\begin{equation}
\nabla h = h_p \nabla p_0 + c_p \nabla T + \sum_k \xi_k \nabla X_k \enskip ,
\end{equation}
giving
\begin{equation}
  \frac{\partial (\rho h)}{\partial t}  = 
 \nabla\cdot \frac{\kth}{c_p}\nabla h -  
 \sum_k \nabla\cdot \frac{\xi_k \kth}{c_p}\nabla X_k -
 \nabla\cdot \frac{h_p \kth}{c_p}\nabla p_0.
  \end{equation}
Compute $\kth^{(1)}, c_p^{(1)}$, and $\xi_k^{(1)}$ from $\rho^{(1)}, T^{(1)}$, and $X_k^{(1)}$ as inputs to the equation of state.  The update is given by
\begin{eqnarray}
(\rho h)^{(2),\star} &=& (\rho h)^{(1a),\star} + \frac{\dt}{2}\nabla\cdot\left(\frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(2),\star} + \frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(2),\star} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{n+1,\star} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{n}\right),
\end{eqnarray}
which is numerically implemented as a diffusion equation for $h^{(2),\star}$,
\begin{eqnarray}
\left(\rho^{(2),\star} - \frac{\dt}{2}\nabla\cdot\frac{\kth^{(1)}}{c_p^{(1)}}\nabla\right)h^{(2),\star} &=& (\rho h)^{(1a),\star} + \frac{\dt}{2}\nabla\cdot\frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(2),\star} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{n+1,\star} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{n}\right),
\end{eqnarray}

>>>>

\begin{itemize}
\item {\bf React State}$[\rho^{\inp},(\rho                                                                   h)^{\inp},X_k^{\inp},T^{\inp}, (\rho\Hext)^{\inp},                                                      
  p_0^{\inp}] \rightarrow [\rho^{\outp}, (\rho h)^{\outp}, X_k^{\outp},                                   
  T^{\outp}, (\rho \omegadot_k)^{\outp}, (\rho\Hnuc)^{\outp}]$
  evolves the species and enthalpy due to reactions through
  $\Delta t/2$ according to:
\begin{equation}
\frac{dX_k}{dt} = \omegadot_k(\rho,X_k,T) ; \qquad
\frac{dT}{dt}   = \frac{1}{c_p} \left ( -\sum_k \xi_k  \omegadot_k  + \Hnuc \right ).
\end{equation}
%This system is solved using the stiff ordinary differential equation                                     
%integration package, {\tt VODE} \citep{vode}.                                                            
Full details of the
solution procedure can be found in Paper III. We then define:
\begin{eqnarray}
(\rho\omegadot_k)^{\outp} &=& \frac{\rho^{\outp} ( X_k^{\outp} - X_k^{\inp})}{\dt/2}, \\
(\rho h)^{\outp} &=& (\rho h)^{\inp} + \frac{\dt}{2} (\rho\Hnuc)^{\outp} + \frac{\dt}{2} (\rho\Hext)^{\in\
p}.
\end{eqnarray}
where the enthalpy update includes external heat sources $(\rho\Hext)^{\inp}$.
As introduced in Paper IV, we update the temperature using $T^{\outp} =                                   
T(\rho^\outp,h^\outp,X_k^\outp)$ for planar geometry or $T^{\outp} =                                      
T(\rho^\outp,p_0^\inp,X_k^\outp)$ for spherical geometry.
Note that the density remains unchanged within {\bf React State}, i.e.,
$\rho^{\outp} = \rho^{\inp}$.

\item {\bf Advect Base Density}$[\rho_0^\inp,w_0^\inp] \rightarrow
  [\rho_0^\outp, \rho_0^{\outp,\nph}]$ is the process by which we
  update the base state density through $\dt$ in time.  We keep the
  time-centered edge states, $\rho_0^{\outp,\nph}$,
  since they are used later in discretization of $\etarho$ for planar problems.
\begin{description}
\item[planar:] We discretize equation (\ref{eq:Base State Density}) to
  compute the new base state density,
\begin{equation}
\rho_{0,j}^{\outp} = \rho_{0,j}^{\inp} - \frac{\dt}{\dr} \left [ \left( \rho_0^{\outp,\nph} w_0^{\inp}\right)_{j+\myhalf} - \left( \rho_0^{\outp,\nph} w_0^{\inp}\right)_{j-\myhalf} \right ].
\end{equation}
  We compute the time-centered edge states, $\rho_0^{\outp,\nph}$,
  by discretizing an expanded form of equation (\ref{eq:Base State Density}):
\begin{equation}
\frac{\partial \rho_0}{\partial t} + w_0 \frac{\partial \rho_0}{\partial r} = - \rho_0 \frac{\partial w_0}{\partial r},
\end{equation}
  where the right hand side is used as the force term.
\item[spherical:] The base state density update now includes the area factors in the 
  divergences:
\begin{equation}
\rho_{0,j}^{\outp} = \rho_{0,j}^{\inp} - \frac{1}{r_j^2} \frac{\dt}{\dr} \left [ \left( r^2 \rho_0^{\outp,\nph} w_0^{\inp}\right)_{j+\myhalf} - \left( r^2 \rho_0^{\outp,\nph} w_0^{\inp}\right)_{j-\myhalf} \right].
\end{equation}
  In order to compute the time-centered edge states, an additional geometric 
  term is added to the forcing, due to the spherical discretization of 
  (\ref{eq:Base State Density}):
\begin{equation}
\frac{\partial \rho_0}{\partial t} + w_0 \frac{\partial \rho_0}{\partial r} = - \rho_0 \frac{\partial w_0}{\partial r} - \frac{2 \rho_0 w_0}{r}.
\end{equation}
\end{description}

\item {\bf Enforce HSE}$[p_0^{\inp},\rho_0^{\inp}]
  \rightarrow [p_0^{\outp}]$ has replaced {\bf Advect Base Pressure}
  from Paper III as the process by which we update the base state
  pressure.  Rather than discretizing the evolution equation for
  $p_0$, we enforce hydrostatic equilibrium directly, which is numerically simpler
  and analytically equivalent.  We first set 
  $p_{0,j=0}^{\outp} = p_{0,j=0}^{\inp}$ and then update $p_0^\outp$ using:
\begin{equation}
p_{0,j+1}^{\outp} = p_{0,j}^{\outp} + \Delta r g_{j+\myhalf}\frac{\left(\rho_{0,j+1}^{\inp}+\rho_{0,j}^{\inp}\right)}{2},
\end{equation}
  where $g=g(\rho_0^\inp)$.  As soon as $\rho_{0,j}^\inp < \rho_{\rm cutoff}$, we set 
  $p_{0,j+1}^\outp = p_{0,j}^\outp$ for all remaining values of $j$.  
  Then we compare $p_{0,j_{\rm max}}^\outp$ with $p_{0,j_{\rm max}}^\inp$ and offset
  every element in $p_0^\outp$ so that $p_{0,j_{\rm max}}^\outp = p_{0,j_{\rm max}}^\inp$.  
  We are effectively using the location where the $\rho_0^\inp$ drops below 
  $\rho_{\rm cutoff}$ as the starting point for integration.

\item {\bf Advect Base Enthalpy}$[(\rho h)_0^\inp,w_0^\inp,\psi^\inp] \rightarrow [(\rho h)_0^\outp]$
  is the process by which we update the base state enthalpy through $\dt$ in time.  
\begin{description}
\item[planar:] We discretize equation (\ref{eq:Base State Enthalpy}), neglecting reaction source terms,
  to compute the new base state enthalpy,
\begin{equation}
(\rho h)_{0,j}^{\outp} = (\rho h)_{0,j}^{\inp} - \frac{\dt}{\Delta r} \left\{ \left[ (\rho h)_0^{\nph} w_0^{\inp}\right]_{j+\myhalf} - \left[ (\rho h)_0^{\nph} w_0^{\inp}\right]_{j-\myhalf} \right\} + \dt\psi_j^{\inp}.
\end{equation}
  We compute the time-centered edge states, $(\rho h)_0^{\nph}$, by discretizing
  an expanded form of equation (\ref{eq:Base State Enthalpy}):
\begin{equation}
\frac{\partial (\rho h)_0}{\partial t} + w_0 \frac{\partial (\rho h)_0}{\partial r} = -(\rho h)_0 \frac{\partial w_0}{\partial r} + \psi.
\end{equation}
\item[spherical:]  The base state enthalpy update now includes the area factors 
  in the divergences:
\begin{eqnarray}
(\rho h)_{0,j}^{\outp} &=& (\rho h)_{0,j}^{\inp} \nonumber \\
&& - \frac{1}{r_j^2} \frac{\dt}{\dr} \left \{ \left[ r^2 (\rho h)_0^{\nph} w_0^{\inp}\right]_{j+\myhalf} - \left[ r^2 (\rho h)_0^{\nph} w_0^{\inp}\right]_{j-\myhalf} \right\} +\dt\psi^{\inp,\nph}.\nonumber\\
\end{eqnarray}
  In order to compute the time-centered edge states, an additional geometric 
  term is added to the forcing, due to the spherical discretization of 
  (\ref{eq:Base State Enthalpy}):
\begin{equation}
\frac{\partial (\rho h)_0}{\partial t} + w_0 \frac{\partial (\rho h)_0}{\partial r} = -(\rho h)_0 \frac{\partial w_0}{\partial r} - \frac{2 (\rho h)_0 w_0}{r} + \psi.
\end{equation}
\end{description}

\item {\bf Computing {\boldmath $w_0$}}\label{Sec:Computing w0}
Here we describe the process by which we compute $w_0$.  The arguments 
are different for planar and spherical geometries.
\begin{description}

@@

\end{itemize}

@@

%-----------------------------------------------------------------------------
\subsection{$\Gamma_1$ Variation Changes}

@@

These can be written more compactly as:
\begin{equation}
\frac{\partial w_0}{\partial r} = \Sbar -\frac{1}{\gammabar p_0}\psi +
\overline{ \left ( \frac{\delta \Gamma_1}{\gammabar^2 p_0} \Ubt \cdotb \nablab
  p_0 \right ) } \enskip , \label{eq:base_w0_with_dgamma1}
\end{equation}
for plane-parallel geometries (analogous to eq. [\ref{eq:divw0}]), and
\begin{equation}
\nablab \cdotb (\beta_0 \Ubt) = \beta_0 \left [ S - \Sbar + \frac{\delta
    \Gamma_1}{\gammabar^2 p_0} \psi + \frac{\delta \Gamma_1}{\gammabar^2 p_0}
  \Ubt \cdotb \nablab p_0 - \overline{ \left ( \frac{\delta
      \Gamma_1}{\gammabar^2 p_0} \Ubt \cdotb \nablab p_0 \right ) } ~ \right ]
 \enskip ,  \label{eq:constraint_with_delta_gamma}
\end{equation}

@@

This change comes into \maestro\ in a variety of steps, summarized here.

\begin{itemize}

\item In {\bf Step 3}, we are doing the ``predictor'' portion of the 
\maestro\ algorithm, getting the MAC velocity that satisfies the constraint, 
so we do not try to incorporate the $\delta \Gamma_1$ effect.  We set
all the $\delta \Gamma_1$ terms in
Eq.~\ref{eq:constraint_with_delta_gamma} to zero.

\item In {\bf Step 6}, we are computing the new time-centered source, 
$S^{\nph,\star}$ and the base state velocity, $w_0^\nph$.  Now we can
incorporate the $\delta \Gamma_1$ effect.  First we construct:
\begin{equation}
\frac{\delta \Gamma_1}{\Gamma_1^2 p_0} \Ubt \cdotb \nablab p_0 \approx
   \frac{\Gamma_1^{n+1,\star} - \overline{\Gamma_1^{n+1,\star}}}
         {{\overline{\Gamma_1^{n+1,\star}}}^2} \frac{1}{p_0^n} \Ubt^n \cdotb \nablab p_0^n
\end{equation}
Then we call {\bf average} to construct the lateral average of this
\begin{equation}
\overline{\frac{\delta \Gamma_1}{\Gamma_1^2 p_0} \Ubt \cdotb \nablab p_0} = 
   \mathbf{Avg} \left (\frac{\Gamma_1^{n+1,\star} - \overline{\Gamma_1^{n+1,\star}}}
         {{\overline{\Gamma_1^{n+1,\star}}}^2} \frac{1}{p_0^n} \Ubt^n \cdotb \nablab p_0^n \right )
\end{equation}

Since the average of this is needed in advancing $w_0$, we modify $\overline{S}$ 
to include this average:
\begin{equation}
\overline{S^{\nph,\star}} \leftarrow \overline{S^{\nph,\star}} + 
   \overline{\frac{\delta \Gamma_1}{\Gamma_1^2 p_0} \Ubt \cdotb \nablab p_0} 
\end{equation}

\item In {\bf Step 7}, we now include the $\delta \Gamma_1$ term in the righthand
side for the constraint by solving:
\begin{equation}
\nabla \cdot \left(\beta_0^{\nph,\star} \uadvtwo\right) =
\beta_0^{\nph,\star}\left( S^{\nph,\star} - \overline{S^{\nph,\star}} +
   \frac{\Gamma_1^{n+1,\star} - \overline{\Gamma_1^{n+1,\star}}} 
         {{\overline{\Gamma_1^{n+1,\star}}}^2} \frac{1}{p_0^n} 
         (\psi^{\nph,\star} + \Ubt^n \cdotb \nablab p_0^n)
\right)
\end{equation}
We note that this includes the average of the correction term as shown
in Eq.~\ref{eq:constraint_with_delta_gamma} because we modified
$\bar{S}$ to include this already.
\end{itemize}

%-----------------------------------------------------------------------------
\subsection{Thermal Diffusion Changes}
Immediately after {\bf Step 4H}, diffuse the enthalpy through 
a time interval of $\dt$.  First, define $(\rho h)^{(1a),\star} = (\rho h)^{(2),\star}$.  
We recompute $(\rho h)^{(2),\star}$ to account for thermal diffusion.  Here we begin
with the enthalpy equation, but consider only the 
diffusion terms,
\begin{equation}
\frac{\partial (\rho h)}{\partial t} = \nabla\cdot\kth\nabla T.
  \end{equation}
We can recast this as an enthalpy-diffusion equation by applying the
chain-rule to $h(p_0,T,X_k)$,
\begin{equation}
\nabla h = h_p \nabla p_0 + c_p \nabla T + \sum_k \xi_k \nabla X_k \enskip ,
\end{equation}
giving
\begin{equation}
  \frac{\partial (\rho h)}{\partial t}  = 
 \nabla\cdot \frac{\kth}{c_p}\nabla h -  
 \sum_k \nabla\cdot \frac{\xi_k \kth}{c_p}\nabla X_k -
 \nabla\cdot \frac{h_p \kth}{c_p}\nabla p_0.
  \end{equation}
Compute $\kth^{(1)}, c_p^{(1)}$, and $\xi_k^{(1)}$ from $\rho^{(1)}, T^{(1)}$, and $X_k^{(1)}$ as inputs to the equation of state.  The update is given by
\begin{eqnarray}
(\rho h)^{(2),\star} &=& (\rho h)^{(1a),\star} + \frac{\dt}{2}\nabla\cdot\left(\frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(2),\star} + \frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(2),\star} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{n+1,\star} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{n}\right),
\end{eqnarray}
which is numerically implemented as a diffusion equation for $h^{(2),\star}$,
\begin{eqnarray}
\left(\rho^{(2),\star} - \frac{\dt}{2}\nabla\cdot\frac{\kth^{(1)}}{c_p^{(1)}}\nabla\right)h^{(2),\star} &=& (\rho h)^{(1a),\star} + \frac{\dt}{2}\nabla\cdot\frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(2),\star} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{n+1,\star} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{n}\right),
\end{eqnarray}
